%-------------------------
% Resume
% Author: Ryan Wallace
% Based off of: https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\definecolor{resumeTimestamp}{gray}{0.62}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\providecommand{\resumeUpdatedAt}{}
\InputIfFileExists{resume-updated-at.tex}{}{}
\fancyfoot[R]{\ifx\resumeUpdatedAt\empty\else\makebox[0pt][r]{\color{resumeTimestamp}\scriptsize Last updated \resumeUpdatedAt}\fi}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\newlength{\resumeFooterWidth}
\setlength{\resumeFooterWidth}{0.97\textwidth}
\addtolength{\resumeFooterWidth}{0.15in}
\setlength{\headwidth}{\resumeFooterWidth}
\setlength{\footskip}{14pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeDetail}[2]{
  \item\small{
    \textit{#1}: #2 \vspace{-1pt}
  }
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7.5pt}}
\newcommand{\resumeDetailListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeDetailListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large Ryan Wallace} \\ \vspace{1.5pt}
    \small Boston, MA $|$ \href{mailto:ryan@ryancswallace.dev}{\nolinkurl{ryan@ryancswallace.dev}} $|$ 617-852-9239 \\
    \href{https://github.com/ryancswallace}{\nolinkurl{github.com/ryancswallace}} $|$
    \href{https://ryancswallace.dev}{\nolinkurl{ryancswallace.dev}} $|$
    \href{https://linkedin.com/in/ryancswallace}{\nolinkurl{linkedin.com/in/ryancswallace}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Harvard University}{Cambridge, MA}
      {A.B. in Computer Science, cum laude; secondary concentration in Statistics; GPA: 3.8.}{May 2018}
      \resumeDetailListStart
        \resumeDetail{Senior Research}{``Modeling Behavior of Networked Agents with Dynamic Opinions''}
        \resumeDetail{Computing Coursework}{Algorithms and Data Structures; Big Data Systems; Artificial Intelligence; Networks, Economics and Computation; Abstraction and Design in Computation.}
        \resumeDetail{Statistics Coursework}{Real Analysis; Probability; Inferential Statistics; Time Series and Prediction; Generalized Linear Models; Econometrics.}
      \resumeDetailListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Federal Reserve Bank of Boston}{Boston, MA}
      {Lead Data Scientist, Research}{January 2023 -- March 2026}
      \resumeItemListStart
        \resumeItem{Designed the architecture and coordinated implementation of an AWS data lakehouse supporting terabyte-scale research datasets and reproducible analytical workflows across the Federal Reserve System.}
        \resumeItem{Built Python/Spark tooling that accelerated terabyte-scale analysis, standardized researcher workflows, and automated administrative operations.}
        \resumeItem{Created and led an internal technical talk series to promote best practices in data science, machine learning, and software engineering.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Senior Data Scientist, Research}{December 2021 -- January 2023}
      \resumeItemListStart
        \resumeItem{Architected and developed a data lake using Spark Streaming for ELT and Airflow for job orchestration.}
        \resumeItem{Categorized debit card transactions on multi-terabyte datasets using text clustering and classification techniques.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Data Scientist, Research}{December 2020 -- December 2021}
      \resumeItemListStart
        \resumeItem{Partnered with economists to produce empirical reports on consumer spending response to the CARES Act. Developed a distributed lag regression model and robustness checks.}
        \resumeItem{Modeled expected effectiveness of the Main Street Lending Program (MSLP) using Fed warehouse data, SQL, scikit-learn, and Plotly.}
      \resumeItemListEnd

    \resumeSubSubheading
      {DevOps Engineer, Research}{December 2019 -- December 2020}
      \resumeItemListStart
        \resumeItem{Completed migration of compute, database, and web service infrastructure to AWS using IaC under CI/CD.}
        \resumeItem{Created data pipelines to continuously update datasets scraped from public sites and retrieved from REST APIs.}
      \resumeItemListEnd

    \vspace{6pt}
    \resumeSubheading
      {Harvard Data Ventures}{Cambridge, MA}
      {President}{December 2017 -- September 2018}
      \resumeItemListStart
        \resumeItem{Provided technical and project management guidance on data science projects for Boston startups.}
        \resumeItem{Led training of fellows in weekly coding workshops, data science seminars, and an industry sponsorship program.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Fellow}{September 2015 -- December 2017}
      \resumeItemListStart
        \resumeItem{Refined project specifications, developed models, completed analyses and simulations, and presented results regularly to clients' technical and business teams.}
      \resumeItemListEnd

    \vspace{6pt}
    \resumeSubheading
      {Arrowstreet Capital}{Boston, MA}
      {Research Intern}{June 2017 -- August 2017}
      \resumeItemListStart
        \resumeItem{Implemented and deployed to production an equity risk analysis module based on a newly published model. Used Numba to achieve a 5-fold execution speedup over baseline.}
        \resumeItem{Applied Bayesian regression and time-series methods to decompose returns and support portfolio risk analysis.}
      \resumeItemListEnd

    \vspace{6pt}
    \resumeSubheading
      {BNY Mellon}{New York, NY}
      {Software Engineering Intern}{June 2016 -- August 2016}
      \resumeItemListStart
        \resumeItem{Developed a tool to predict the likelihood of sales conversions using an ensemble model. Enabled BNY's sales team to sort and filter leads by estimated potential.}
        \resumeItem{Implemented a Salesforce client in Apex to consume and process REST API data from BNY's proprietary sales platform.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python; SQL; Go; Bash; C; OCaml.} \\
     \vspace{3.5pt}
     \textbf{Data \& ML Platforms}{: Spark; Airflow; AWS data lakehouse architecture; OLAP systems; stream processing; relational and key-value databases.} \\
     \vspace{3.5pt}
     \textbf{Modeling \& Applied ML}{: Generalized linear models; Bayesian regression; time-series analysis; text clustering and classification; search and matching; model explanation; LLM application development.} \\
     \vspace{3.5pt}
     \textbf{ML Ops \& Infrastructure}{: Model serving with Ollama and vLLM; Docker; Terraform; Ansible; Linux (RHEL, Alma); CI/CD; REST APIs; system administration automation; Git.} \\
     \vspace{3.5pt}
     \textbf{Observability}{: Prometheus; Grafana; CloudWatch.} \\
     \vspace{3.5pt}
     \textbf{Engineering Practices}{: Object-oriented and functional programming; agile development; production data tooling; technical project management.}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
